\documentclass{article}
\usepackage[margin=1in]{geometry}
\title{The Hockey Sweater}
\author{by Roch Carrier}
\begin{document}
\maketitle

The winters of my childhood were long, long seasons.

We lived in three places: the school, the church, and the lab.
But our real life was in the lab.
Real battles were won in the lab.
Real strength appeared in the lab.
The real leaders showed themselves in the lab.
School was a sort of punishment.
Professors always want to punish students and school is their most natural way of punishing us.
However, school was also a quiet place where we could prepare for the next experiment.
Lay our our next strategies.
As for church, we found there the tranquillity of God.
There, we forgot school and dreamed about the next experiment.
Through our daydreams it might happen that we would recite a prayer;
we would ask God to help us pipette as well as Irwin Rose.

We all wore the same uniform as Irwin Rose: 
a normal lab coat.
We all combed our hair in the same style as Irwin Rose, 
which was easy because he had very little hair.
We vortexed our samples like Maurice Richard.
We popped off our pipette tips like Maurice Richard.
We cut all his pictures out of the newspapers and pasted them into an MS Paint collage.

In the lab, when we had our time on the microscope, the students would fight each other for their chance to use it.
We were five Irwin Roses taking it away from five other Irwin Roses.
We were ten grad students, all of us wearing, with the same blazing enthusiasm, the uniform of the UCI Anteaters (a lab coat).
On our backs, we all wore no symbols, because embroidery can only be approved by EH&S.

\end{document}
